Fail Faster

### 2025-03-25 paper/paper.tex
TERRIBLE DATA ERROR

In addition to \camlname's overall bug-finding speed, we evaluate
the performance of its type-derived generators---specifically,
whether they can transform previously intractable tasks into
tractable ones. Out of 78 tasks that initially timed out,
30 (38.4\%) completed successfully using \camlname alone, and
50 (64.1\%) completed successfully after adding \csplitmix.
This shows that staged type-derived generators can provide
significant performance improvements for free, without
 any additional effort from the user.

>>>>

In addition to \camlname's overall bug-finding speed, we evaluate
the performance of its type-derived generators---specifically,
whether they can transform previously intractable tasks into
tractable ones. Out of 79 tasks that initially timed out,
31 (38.4\%) completed successfully using \camlname alone, and
51 (64.1\%) completed successfully after adding \csplitmix.
This shows that staged type-derived generators can provide
significant performance improvements for free, without
 any additional effort from the user.
